---
title: "Inverted Faces Analysis, Attenion Modulation"
author: "Casey Jayne"
date: "9/11/2019"
output: 
  html_document:
    df_print: paged
    toc: TRUE
---

```{r libs, include=FALSE}
require("ggplot2")
#require(GGally)
require(reshape2)
require(lme4)
require(lattice)
require(dplyr)
require(tidyverse)
require("haven")
require(lsr)
require(plyr)
require(car)
#require(fitdistrplus)
#require(multcomp)
#library(lmerTest)
library(latticeExtra)  
library(markdown)
library(knitr)
require(lubridate)
library(glue)
library(readr)
```

R Markdown, Statistical Analysis for Navon/Inverted faces Pilot Study, Attention Modulation Intervention 
 Feusner 2019

```{r dataimport, include=FALSE}
#import all IF files as a DF
inputdir='/Users/casey/Desktop/navonanalysis-master/data/source/attmod'
files=list.files(path='/Users/casey/Desktop/navonanalysis-master/data/source/attmod',
                 pattern="*task-invertedfaces(.*)csv$", recursive = T, full.names = TRUE)
invertlist=lapply(files, read.csv)
invertdf=do.call(rbind, invertlist)
str(invertdf)
outputdir='/Users/casey/Desktop/navonanalysis-master/data/derivatives/attmod'
numsubs=3 #total number subjects
numses=2 #total number of sessions

####################DATA CLEANING ########################################
#subset only the LONG trials
invertdf=subset(invertdf, Time=='l')
invertdf[["Time"]] #just checking

#add task column
invertdf$task=rep("invertedfaces", length(invertdf$Subject))
#add intervention column
invertdf$intervention=rep("attmod", length(invertdf$Subject))
#add Trial counter Column for only the long
invertdf$trial=factor(rep(seq(1, length(invertdf$Session)/(numsubs*numses)), numsubs))

#subset, select, and factor relevant portions
#using the subsetted trial counter rather than original
invertdf=subset(invertdf, select=c(Subject, Session, task, intervention, trial, Direction, 
                                   Comparison.ACC, Comparison.RT))
invertdf=within(invertdf, {
  Subject=factor(Subject)
  Session=factor(Session)
  trial=factor(trial)
  task=factor(task)})
str(invertdf)

#recode non-repsponse as NA response time
sum(invertdf$Comparison.RT=="0") #checking amount
is.na(invertdf$Comparison.RT)=invertdf$Comparison.RT=="0" #recode
is.na(invertdf$Comparison.ACC)=is.na(invertdf$Comparison.RT) #recode
sum(is.na(invertdf$Comparison.ACC)) #checking nonresponse
sum(invertdf$Comparison.ACC=="0", na.rm=T) #check that nonresponse different than inacc

#add column for log RT
invertdf$logRT=log(invertdf$Comparison.RT)
sum(is.na(invertdf$logRT) && !is.na(invertdf$Comparison.RT)) #check no new NAs created
```

# Simple Statistics, All Responses regardless of ACC

```{r, functions, include=FALSE}
###Save functions of interest
funs=list(mean = ~mean(., na.rm=TRUE), sd = ~sd(., na.rm = TRUE))

```

Check where we are

```{r, allrespcheck, echo=FALSE}
g=sum(invertdf$Comparison.ACC==0, na.rm = T) #55
w=sum(invertdf$Comparison.ACC==1, na.rm = T) #485
q=(length(invertdf$logRT)-sum(is.na(invertdf$logRT))) #1327 [total should be the 2 above]
ifelse (q!=g+w, 
        glue('RT CODED WRONG check output'),
        glue('RT coded for all responses'))
```

## Separated by Switch/Nonswitch
Create a DataFrame include an "Overall" Statistical Output
Separated by Inverted or Upright Viewing Condition and Session Number

```{r, simpleinvert, echo=FALSE, warning=FALSE}
Allresp_temp1= invertdf %>%
  group_by(Subject, Session, Direction) %>%
  summarise_at(c("Comparison.ACC", "logRT"), funs)
Allresp_temp2=invertdf %>%
  group_by(Session, Direction) %>%
  summarise_at(c("Comparison.ACC", "logRT"), funs)
Allresp_Istats=bind_rows(Allresp_temp1, Allresp_temp2)
Allresp_Istats$Subject=ifelse(is.na(Allresp_Istats$Subject), "Overall", 
                             Allresp_Istats$Subject)
#rm(Allresp_temp1, Allresp_temp2)
```
```{r, include=TRUE, cols.print=7, rows.print=24}
print(Allresp_Istats)
```

# Repeated Measures Anovas, All Responses regardless of Accuracy
## RT by Inverted/Upright

```{r, invertrtanova, include=TRUE}
summary(aov(logRT~Direction+Error(Subject*Session/Direction), data=invertdf))
summary(lmer(logRT~1+Direction+Session+Direction:Session+(1+Session|Subject), data=invertdf))
anova(lmer(logRT~1+Direction+Session+Direction:Session+(1+Session|Subject), data=invertdf))
```

## ACC by Inverted/Upright

```{r, invertaccanova}
summary(aov(Comparison.ACC~Direction+Error(Subject*Session/Direction), data=invertdf))
#lmer
summary(lmer(Comparison.ACC~1+Direction+Session+Direction:Session+(1+Session|Subject), data=invertdf))
anova(lmer(Comparison.ACC~1+Direction+Session+Direction:Session+(1+Session|Subject), data=invertdf))
```

## Graphs, only Accurate RTs

```{r, include=TRUE, echo=FALSE}
#Graphs
#RT
xyplot(logRT_mean~Session|Subject, 
       data=Allresp_temp1, 
       groups=Direction, 
       h=Allresp_temp1$logRT_mean,
       auto.key =list(space="right", col=c("blue", "pink"), text=c("Inverse", "Upright")), 
       main="Response Time by Subject", 
       ylab = "Response Time",
       scales=list(alternating=FALSE),
       panel = function(x, y, h, subscripts, groups) {
         panel.lmline(x, y, lty=3, lwd=1, col="purple")
         panel.abline(mean(h), lty=1, col="red")
         llines(x=x, y=y, type='p', pch=c(23, 21, 23, 21), col=c("blue", "pink"),
                fill=c("blue", "pink"))
         #ltext(x = x, y = y,labels = c("G", "L", "G", "L"), cex=1,
         #fontfamily = "HersheySans", col=c("blue", "pink"))
       },
       layout=c(5,1), aspect=5,
       axis=axis.grid
)
```

### ACC
```{r, include=TRUE, echo=FALSE}
#ACC
xyplot(Comparison.ACC_mean~Session|Subject, 
       data=Allresp_temp1, 
       groups=Direction, 
       h=Allresp_temp1$Comparison.ACC_mean,
       auto.key =list(space="right", col=c("blue", "pink"), text=c("Inverse", "Upright")), 
       main="Accuracy by Subject", 
       ylab = "Accuracy",
       scales=list(alternating=FALSE),
       panel = function(x, y, h, subscripts, groups) {
         panel.lmline(x, y, lty=3, lwd=1, col="purple")
         panel.abline(mean(h), lty=1, col="red")
         llines(x=x, y=y, type='p', pch=c(23, 21, 23, 21), col=c("blue", "pink"),
                fill=c("blue", "pink"))
         #ltext(x = x, y = y,labels = c("G", "L", "G", "L"), cex=1,
         #fontfamily = "HersheySans", col=c("blue", "pink"))
       },
       layout=c(5,1), aspect=5,
       axis=axis.grid
)
```

# Simple Stats including only ACC answers for RT
Check where we are 
```{r, checkallacc, echo=FALSE}
#recode ACC=0 as RT=NA 
sum(is.na(invertdf$logRT))
is.na(invertdf$logRT)=invertdf$Comparison.ACC==0
sum(is.na(invertdf$logRT)) #checking
sum(is.na(invertdf$Comparison.ACC)) #now should be less NA for ACC than RT (showing incorrect are also NA RT)

##check where we are
w=sum(invertdf$Comparison.ACC==1, na.rm = T) #1297
q=length(invertdf$logRT)-sum(is.na(invertdf$logRT)) #1327 [total should be the 2 above]
ifelse (q!=w, 
        glue('RT CODED WRONG check output'),
        glue('RT coded only for correct responses'))
```


## Separated by Inverted/Upright Condition
Create a DataFrame include an "Overall" Statistical Output
Separated by Inverted/Upright Viewing Condition and Session Number

```{r, simpleaccinvert, include=FALSE, warning=FALSE}
###Simple Statistics
Allaccresp_temp1= invertdf %>%
  group_by(Subject, Session, Direction) %>%
  summarise_at(c("Comparison.ACC", "logRT"), funs)
Allaccresp_temp2=invertdf %>%
  group_by(Session, Direction) %>%
  summarise_at(c("Comparison.ACC", "logRT"), funs)
Allaccresp_Istats=bind_rows(Allaccresp_temp1, Allaccresp_temp2)
Allaccresp_Istats$Subject=ifelse(is.na(Allaccresp_Istats$Subject), "Overall", 
                                 Allaccresp_Istats$Subject)
#rm(Allaccresp_temp1, Allaccresp_temp2)
```

## Graph RT only ACC responses
```{r, include=TRUE, echo=FALSE}
#RT, only accurate
xyplot(logRT_mean~Session|Subject, 
       data=Allaccresp_temp1, 
       groups=Direction, 
       h=Allaccresp_temp1$logRT_mean,
       auto.key =list(space="right", col=c("blue", "pink"), text=c("Inverse", "Upright")), 
       main="Response Time by Subject", 
       ylab = "Response Time",
       scales=list(alternating=FALSE),
       panel = function(x, y, h, subscripts, groups) {
         panel.lmline(x, y, lty=3, lwd=1, col="purple")
         panel.abline(mean(h), lty=1, col="red")
         llines(x=x, y=y, type='p', pch=c(23, 21, 23, 21), col=c("blue", "pink"),
                fill=c("blue", "pink"))
         #ltext(x = x, y = y,labels = c("G", "L", "G", "L"), cex=1,
         #fontfamily = "HersheySans", col=c("blue", "pink"))
       },
       layout=c(5,1), aspect=5,
       axis=axis.grid
)
```

# Only Accurate Responses Response Times Anova/GLMMs
## RT by Invert/Upright

```{r, invertrtaccanova, include=TRUE}
summary(aov(logRT~Direction+Error(Subject*Session/Direction), data=invertdf))
#lmer
summary(lmer(logRT~1+Direction+Session+Direction:Session+(1+Session|Subject), data=invertdf))
anova(lmer(logRT~1+Direction+Session+Direction:Session+(1+Session|Subject), data=invertdf))
```
