---
title: "Navon_FastFace_Statsonly"
author: "Casey Jayne"
date: "8/12/2019"
output: 
  html_document:
    df_print: paged
    toc= TRUE
---

```{r libs, include=FALSE}
require("ggplot2")
#require(GGally)
require(reshape2)
require(lme4)
require(lattice)
require(dplyr)
require(tidyverse)
require("haven")
require(lsr)
require(plyr)
require(car)
#require(fitdistrplus)
#require(multcomp)
#library(lmerTest)
library(latticeExtra)  
library(markdown)
library(knitr)
require(lubridate)
library(glue)
library(readr)
```

 R Markdown, Statistical Analysis for Navon/Inverted faces Pilot Study, Fast Face Intervention 
 Feusner 2019

```{r dataimport, include=FALSE}
#import all navon files as a DF
inputdir='/Users/casey/Desktop/navonanalysis-master/data/source/fast'
files=list.files(path='/Users/casey/Desktop/navonanalysis-master/data/source/fast',
                pattern="*task-navon(.*)csv$", recursive = T, full.names = TRUE)
navonlist=lapply(files, read.csv)
navondf=do.call(rbind, navonlist)
str(navondf)
outputdir='/Users/casey/Desktop/navonanalysis-master/data/derivatives/fast'
numsubs=5 #total number subjects
numses=2 #total number of sessions

#remove practice block
navondf=navondf[!navondf$Block=="P",]
sum(navondf$Block=="P")
str(navondf) 

#fix labels, dataset specific
#some subjects labeled incorrectly, fix these
navondf$Subject[navondf$Subject=="5031"]="50312"
navondf$Subject[navondf$Subject=="501421"]="50142"
navondf$Subject[navondf$Subject=="5020"]="50202"
sum(navondf$Subject=="5031" || navondf$Subject=="501421" || navondf$Subject=="5020") 
#make sure no subjects exist with old label (total should be zero)

#add task column for export if grand DF ever desired
navondf$task=rep("navon", length(navondf$Subject))
#add group column for export if grand DF ever desired
navondf$intervention=rep("fastface", length(navondf$Subject))

#add Trial counter Column
temp1=length(navondf$Session)/(numsubs*numses)
navondf$trial=factor(rep(seq(1, length(navondf$Session)/(numsubs*numses)), numsubs))

#Remove irrelevant variables columns and reorder
navondf=subset(navondf, select= c(Subject, Session, task, intervention, trial, TargetLocation, 
                                  Configuration, Stimuli.ACC, Stimuli.RT))

#change needed columns to factors for grouping
navondf=within(navondf, {
  Session=as.factor(Session)
  Subject=as.factor(Subject)
  task=as.factor(task)
  
})
str(navondf)

#recode non-repsponse as NA response time
sum(navondf$Stimuli.RT=="0") #checking amount (28)
is.na(navondf$Stimuli.RT)=navondf$Stimuli.RT=="0" #recode
is.na(navondf$Stimuli.ACC)=is.na(navondf$Stimuli.RT) #recode
sum(is.na(navondf$Stimuli.ACC)) #checking nonresponse (now there are 28)
sum(navondf$Stimuli.ACC=="0", na.rm=T) #check that nonresponse different than inacc

#add column for RT log (for calculations)
navondf$logRT=log(navondf$Stimuli.RT)
sum(is.na(navondf$logRT) && !is.na(navondf$Stimuli.RT)) #check that no new NAs created

#make additional switch/nonswitch condition (based on configuration)
navondf$Switch=as.factor(ifelse(navondf$Configuration=="GLS" |
                        navondf$Configuration=="LGS", "switch", "nonswitch"))

```

# Simple Statistics, All Responses regardless of ACC

```{r, functions, include=FALSE}
###Save functions of interest
funs=list(mean = ~mean(., na.rm=TRUE), sd = ~sd(., na.rm = TRUE))

```

Check where we are

```{r, allrespcheck, echo=FALSE}
g=sum(navondf$Stimuli.ACC==0, na.rm = T)#53
w=sum(navondf$Stimuli.ACC==1, na.rm = T) #1227
q=length(navondf$logRT)-sum(is.na(navondf$logRT)) #1280 [total should be the 2 above]
ifelse (q!=g+w, 
        glue('RT CODED WRONG {\n}check output'),
        glue('RT coded for all responses'))
```

## Separated by Switch/Nonswitch
Create a DataFrame include an "Overall" Statistical Output
Separated by Switch/NonSwitch Viewing Condition and Session Number

```{r, simpleswitch, echo=FALSE, warning=FALSE}
Allresp_switch_temp1= navondf %>%
  group_by(Subject, Session, Switch) %>%
  summarise_at(c("Stimuli.ACC", "logRT"), funs)
Allresp_switch_temp2=navondf %>%
  group_by(Session, Switch) %>%
  summarise_at(c("Stimuli.ACC", "logRT"), funs)
Allresp_switch_stats=bind_rows(Allresp_switch_temp1, Allresp_switch_temp2)
Allresp_switch_stats$Subject=ifelse(is.na(Allresp_switch_stats$Subject), "Overall", 
                                    Allresp_switch_stats$Subject)
#rm(Allresp_switch_temp1, Allresp_switch_temp2)
```
```{r, include=TRUE, cols.print=7, rows.print=24}
print(Allresp_switch_stats)
```

## Separated by Global/Local positioning
Create a DataFrame include an "Overall" Statistical Output
Separated by Target Location (Global/Local) and Session Number

```{r, simpletagetlocation, echo=FALSE, warning=FALSE}
Allresp_localglobal_temp1= subset(navondf, 
                                  select=c(Subject, Session, TargetLocation, Stimuli.ACC, logRT)) %>%
  group_by(Subject, Session, TargetLocation) %>%
  summarise_at(c("Stimuli.ACC", "logRT"), funs)
Allresp_localglobal_temp2=navondf %>%
  group_by(Session, TargetLocation) %>%
  summarise_at(c("Stimuli.ACC", "logRT"), funs)
Allresp_localglobal_stats=bind_rows(Allresp_localglobal_temp1, Allresp_localglobal_temp2)
Allresp_localglobal_stats$Subject=ifelse(is.na(Allresp_localglobal_stats$Subject), "Overall", 
                                    Allresp_localglobal_stats$Subject)
#rm(Allresp_localglobal_temp1, Allresp_localglobal_temp2)
```
```{r, include=TRUE, cols.print=7, rows.print=24}
print(Allresp_localglobal_stats)
```

## Graph All Answered Questions
### Response Time, Switch
```{r, include=TRUE, echo=FALSE}
xyplot(logRT_mean~Session|Subject, 
       data=Allresp_switch_temp1, 
       groups=Switch, 
       h=Allresp_switch_temp1$logRT_mean,
       auto.key =list(space="right", col=c("blue", "pink")), 
       main="Response Time by Subject", 
       ylab = "Response Time",
       scales=list(alternating=FALSE),
       panel = function(x, y, h, subscripts, groups) {
         panel.lmline(x, y, lty=3, lwd=1, col="purple")
         panel.abline(mean(h), lty=1, col="red")
         llines(x=x, y=y, type='p', pch=c(23, 21,23, 21), col=c("blue", "pink", "blue", "pink"),
                fill=c("blue", "pink", "blue", "pink"))
         #ltext(x = x, y = y,labels = c("G", "L", "G", "L"), cex=1,
         #fontfamily = "HersheySans", col=c("blue", "pink", "blue", "pink"))
       },
       layout=c(5,1), aspect=5,
       axis=axis.grid
)
```

### ACC, Switch
```{r, include=TRUE, echo=FALSE}
xyplot(Stimuli.ACC_mean~Session|Subject, 
       data=Allresp_switch_temp1, 
       groups=Switch, 
       h=Allresp_switch_temp1$logRT_mean,
       auto.key =list(space="right", col=c("blue", "pink")), 
       main="Accuracy by Subject", 
       ylab = "Accuracy",
       scales=list(alternating=FALSE),
       panel = function(x, y, h, subscripts, groups) {
         panel.lmline(x, y, lty=3, lwd=1, col="purple")
         panel.abline(mean(h), lty=1, col="red")
         llines(x=x, y=y, type='p', pch=c(23, 21,23, 21), col=c("blue", "pink", "blue", "pink"),
                fill=c("blue", "pink", "blue", "pink"))
         #ltext(x = x, y = y,labels = c("G", "L", "G", "L"), cex=1,
         #fontfamily = "HersheySans", col=c("blue", "pink", "blue", "pink"))
       },
       layout=c(5,1), aspect=5,
       axis=axis.grid
)
```


### RT, Target Location
```{r, include=TRUE, echo=FALSE}
xyplot(logRT_mean~Session|Subject, 
       data=Allresp_localglobal_temp1, 
       groups=TargetLocation, 
       h=Allresp_localglobal_temp1$logRT_mean,
       auto.key =list(space="right", col=c("blue", "pink")), 
       main="Response Time by Subject", 
       ylab = "Response Time",
       scales=list(alternating=FALSE),
       panel = function(x, y, h, subscripts, groups) {
         panel.lmline(x, y, lty=3, lwd=1, col="purple")
         panel.abline(mean(h), lty=1, col="red")
         llines(x=x, y=y, type='p', pch=c(23, 21,23, 21), col=c("blue", "pink", "blue", "pink"),
                fill=c("blue", "pink", "blue", "pink"))
         #ltext(x = x, y = y,labels = c("G", "L", "G", "L"), cex=1,
         #fontfamily = "HersheySans", col=c("blue", "pink", "blue", "pink"))
       },
       layout=c(5,1), aspect=5,
       axis=axis.grid
)
```

### ACC, Target Location
```{r, include=TRUE, echo=FALSE}
xyplot(Stimuli.ACC_mean~Session|Subject, 
       data=Allresp_localglobal_temp1, 
       groups=TargetLocation, 
       h=Allresp_localglobal_temp1$logRT_mean,
       auto.key =list(space="right", col=c("blue", "pink")), 
       main="Accuracy by Subject", 
       ylab = "Accuracy Time",
       scales=list(alternating=FALSE),
       panel = function(x, y, h, subscripts, groups) {
         panel.lmline(x, y, lty=3, lwd=1, col="purple")
         panel.abline(mean(h), lty=1, col="red")
         llines(x=x, y=y, type='p', pch=c(23, 21,23, 21), col=c("blue", "pink", "blue", "pink"),
                fill=c("blue", "pink", "blue", "pink"))
         #ltext(x = x, y = y,labels = c("G", "L", "G", "L"), cex=1,
         #fontfamily = "HersheySans", col=c("blue", "pink", "blue", "pink"))
       },
       layout=c(5,1), aspect=5,
       axis=axis.grid
)
```

# Repeated Measures Anovas, All Responses regardless of Accuracy
## RT by Switch/Non-Switch

```{r, switchrtanova, include=TRUE}
summary(aov(logRT~Switch+Error(Subject*Session/Switch), data=navondf))
summary(lmer(logRT~1+Switch+Session+Switch:Session+(1+Session|Subject), data=navondf)) 
anova(lmer(logRT~1+Switch+Session+Switch:Session+(1+Session|Subject), data=navondf))
```

## RT by Global/Local
```{r, targetlocrtanova}
summary(aov(logRT~TargetLocation+Error(Subject*Session/TargetLocation), data=navondf))
summary(lmer(logRT~1+TargetLocation+Session+TargetLocation:Session+(1+Session|Subject), data=navondf)) 
anova(lmer(logRT~1+TargetLocation+Session+TargetLocation:Session+(1+Session|Subject), data=navondf))
```

## ACC by Switch/Non-Switch
```{r, switchaccanova}
summary(aov(Stimuli.ACC~Switch+Error(Subject*Session/Switch), data=navondf))
summary(lmer(Stimuli.ACC~1+Switch+Session+Switch:Session+(1+Session|Subject), data=navondf)) 
anova(lmer(Stimuli.ACC~1+Switch+Session+Switch:Session+(1+Session|Subject), data=navondf))
```

## ACC by Global/Local
```{r, targetlocaccanova}
summary(aov(Stimuli.ACC~TargetLocation+Error(Subject*Session/TargetLocation), data=navondf))
summary(lmer(Stimuli.ACC~1+TargetLocation+Session+TargetLocation:Session+(1+Session|Subject), data=navondf)) 
anova(lmer(Stimuli.ACC~1+TargetLocation+Session+TargetLocation:Session+(1+Session|Subject), data=navondf))
```

# Simple Stats including only ACC answers for RT
Check where we are 
```{r, checkallacc, echo=FALSE}
#recode ACC=0 as RT=NA 
sum(is.na(navondf$logRT))
is.na(navondf$logRT)=navondf$Stimuli.ACC==0
sum(is.na(navondf$logRT)) #checking
sum(is.na(navondf$Stimuli.ACC)) #now should be less NA for ACC than RT (showing incorrect are also NA RT)
##check where we are
w=sum(navondf$Stimuli.ACC==1, na.rm = T) #1297
q=length(navondf$logRT)-sum(is.na(navondf$logRT)) #1327 [total should be the 2 above]
ifelse (q!=w, 
        glue('RT CODED WRONG {\n}check output'),
        glue('RT coded only for correct responses'))
```

## Separated by Switch/Nonswitch Condition
Create a DataFrame include an "Overall" Statistical Output
Separated by Switch/NonSwitch Viewing Condition and Session Number

```{r, simpleaccswitch, include=FALSE, warning=FALSE}
Allresp_switch_temp1= navondf %>%
  group_by(Subject, Session, Switch) %>%
  summarise_at(c("Stimuli.ACC", "logRT"), funs)
Allresp_switch_temp2=navondf %>%
  group_by(Session, Switch) %>%
  summarise_at(c("Stimuli.ACC", "logRT"), funs)
Allaccresp_switch_stats=bind_rows(Allresp_switch_temp1, Allresp_switch_temp2)
Allaccresp_switch_stats$Subject=ifelse(is.na(Allaccresp_switch_stats$Subject), "Overall", 
                                    Allaccresp_switch_stats$Subject)
rm(Allresp_switch_temp1, Allresp_switch_temp2)
```
```{r, echo=FALSE}
print(Allaccresp_switch_stats)
```

## Separated by Global/Local positioning
Create a DataFrame include an "Overall" Statistical Output
Separated by Target Location (Global/Local) and Session Number
```{r, simpleaccGL, include=FALSE, warning=FALSE}
Allresp_localglobal_temp1= navondf %>%
  group_by(Subject, Session, TargetLocation) %>%
  summarise_at(c("Stimuli.ACC", "logRT"), funs)
Allresp_localglobal_temp2=navondf %>%
  group_by(Session, TargetLocation) %>%
  summarise_at(c("Stimuli.ACC", "logRT"), funs)
Allaccresp_localglobal_stats=bind_rows(Allresp_localglobal_temp1, Allresp_localglobal_temp2)
Allaccresp_localglobal_stats$Subject=ifelse(is.na(Allaccresp_localglobal_stats$Subject), "Overall", 
                                         Allaccresp_localglobal_stats$Subject)
#rm(Allresp_localglobal_temp1, Allresp_localglobal_temp2)
```
```{r, echo=FALSE}
print(Allaccresp_localglobal_stats)
```

# Only Accurate Responses Response Times Anova/GLMMs
## RT by Switch/Non-Switch

```{r, switchrtaccanova, include=TRUE}
summary(aov(logRT~Switch+Error(Subject*Session/Switch), data=navondf))
summary(lmer(logRT~1+Switch+Session+Switch:Session+(1+Session|Subject), data=navondf)) 
anova(lmer(logRT~1+Switch+Session+Switch:Session+(1+Session|Subject), data=navondf))
```

## RT by Target Location
```{r, include=TRUE}
summary(aov(logRT~TargetLocation+Error(Subject*Session/TargetLocation), data=navondf))
#lmer
summary(lmer(logRT~1+TargetLocation+Session+TargetLocation:Session+(1+Session|Subject), data=navondf)) 
anova(lmer(logRT~1+TargetLocation+Session+TargetLocation:Session+(1+Session|Subject), data=navondf))
```

## Graph, Only ACC response times
### Response Time, Switch
```{r, include=TRUE, echo=FALSE}
xyplot(logRT_mean~Session|Subject, 
       data=Allresp_switch_temp1, 
       groups=Switch, 
       h=Allresp_switch_temp1$logRT_mean,
       auto.key =list(space="right", col=c("blue", "pink")), 
       main="Response Time by Subject", 
       ylab = "Response Time",
       scales=list(alternating=FALSE),
       panel = function(x, y, h, subscripts, groups) {
         panel.lmline(x, y, lty=3, lwd=1, col="purple")
         panel.abline(mean(h), lty=1, col="red")
         llines(x=x, y=y, type='p', pch=c(23, 21,23, 21), col=c("blue", "pink", "blue", "pink"),
                fill=c("blue", "pink", "blue", "pink"))
         #ltext(x = x, y = y,labels = c("G", "L", "G", "L"), cex=1,
         #fontfamily = "HersheySans", col=c("blue", "pink", "blue", "pink"))
       },
       layout=c(5,1), aspect=5,
       axis=axis.grid
)
```

### RT, Target Location
```{r, include=TRUE, echo=FALSE}
xyplot(logRT_mean~Session|Subject, 
       data=Allresp_localglobal_temp1, 
       groups=TargetLocation, 
       h=Allresp_localglobal_temp1$logRT_mean,
       auto.key =list(space="right", col=c("blue", "pink")), 
       main="Response Time by Subject", 
       ylab = "Response Time",
       scales=list(alternating=FALSE),
       panel = function(x, y, h, subscripts, groups) {
         panel.lmline(x, y, lty=3, lwd=1, col="purple")
         panel.abline(mean(h), lty=1, col="red")
         llines(x=x, y=y, type='p', pch=c(23, 21,23, 21), col=c("blue", "pink", "blue", "pink"),
                fill=c("blue", "pink", "blue", "pink"))
         #ltext(x = x, y = y,labels = c("G", "L", "G", "L"), cex=1,
         #fontfamily = "HersheySans", col=c("blue", "pink", "blue", "pink"))
       },
       layout=c(5,1), aspect=5,
       axis=axis.grid
)
```

